Logarithmic Space Verifiers on NP-complete

### 2019-11-12 doc/manuscript.tex
Updated the content proof

\section{Motivation}

@@

\section{Preliminaries}

@@

\section{Hypothesis}

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}. On the one hand, we call the deterministic logarithmic space reduction as $\textit{L-reduction}$. On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL-reduction}$.

@@

\section{Consequences}

@@

Now, we define two classes defined under $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively.

@@

@@

\begin{proof}
 We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L-reduction}$ and $\textit{NL-reduction}$, respectively. Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L-reduction}$ or $\textit{NL-reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.

On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read continuously in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ \cite{HM81}. Therefore, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@

@@

This work is implemented into a Project programmed in Scala \cite{FV19}. In this Project, we use the Assertion on the properties of the instances of each problem and the Unit Test for checking the correctness of every reduction \cite{FV19}. We need to install JDK 8 in order to test the Scala Project \cite{OD16}. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.

\section{Conclusion}

@@

Moreover, Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.

>>>>

@@

\subsection{Preliminaries}

@@

\subsection{Hypothesis}

@@

A logarithmic space transducer is a Turing machine with a read-only input tape, a write-only output tape, and read/write work tapes \cite{MS06}. The work tapes must contain at most $O(\log n)$ symbols \cite{MS06}. A logarithmic space transducer $M$ computes a function $f : \Sigma^{*} \rightarrow \Sigma^{*}$, where $f(w)$ is the string remaining on the output tape after $M$ halts when it is started with $w$ on its input tape \cite{MS06}. We call $f$ a logarithmic space computable function \cite{MS06}. We say that a language $L_{1} \subseteq \{0, 1\}^{*}$ is logarithmic space reducible to a language $L_{2} \subseteq \{0, 1\}^{*}$, written $L_{1} \leq_{l} L_{2}$, if there exists a logarithmic space computable function $f : \{0, 1\}^{*} \rightarrow \{0, 1\}^{*}$ such that for all $x \in \{0, 1\}^{*}$,
\[x \in L_{1} \textit{ if and only if } f(x) \in L_{2}.\]
The logarithmic space reduction is frequently used for $L$ and $NL$ \cite{Pap03}. On the one hand, we call the deterministic logarithmic space reduction as $\textit{L--reduction}$. On the other hand, we call the nondeterministic logarithmic space reduction as $\textit{NL--reduction}$.

@@

\subsection{Consequences}

@@

Now, we define two classes defined under $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively.

@@

Let $\textit{1TAPE}[T(n)]$ denote the family of languages accepted by deterministic one-way Turing machines with $T(n)$ work tape \cite{HM81}.

\begin{theorem}
\label{closed}
If $T(n)$ is such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\] 
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some arbitrary number $k > 1$ which mostly depends from the original instance, that is the result of reading consecutively the symbols in the input tape in a sequential way. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$. However, we know in that instance of size at most $k \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language. In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some arbitrary number $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition. Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some arbitrary number $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every sparse function $T(n)$.
\end{proof}

\begin{theorem}
\label{partially}
$1L \neq 1NL$ under deterministic two-way logarithmic space reduction.
\end{theorem}

\begin{proof} 
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when 
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. Consequently, this is a direct result of Theorem \ref{closed}.
\end{proof}

@@

\begin{proof}
 We obtain that $2L \subseteq L$ and $2NL \subseteq NL$ by the definition of $L$ and $NL$ under the $\textit{L--reduction}$ and $\textit{NL--reduction}$, respectively. Certainly, since the output string will be in $1L$ or $1NL$, then we do not need to reset the computation of the $\textit{L--reduction}$ or $\textit{NL--reduction}$ in order to be decided by a deterministic or nondeterministic logarithmic space Turing machine under logarithmic space composition, respectively.

On the one hand, every language in $L_{1} \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language in $L_{2} \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

In this way, if $L = NL$ then $2L = 2NL$. However, we know that $2L \neq 2NL$ because of $1L \neq 1NL$ under deterministic two-way logarithmic space reduction according to the Theorem \ref{partially}. Indeed, in case of $2L = 2NL$, then every language in $1NL$ is deterministic two-way logarithmic space reduced to a language in $1L$ and viceversa. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

@@

\subsection{Codes}

This work is implemented into a Project programmed in Scala \cite{FV19}. We need to install JDK 8 in order to test the Scala Project \cite{OD16}. In addition, we need to install SBT to run the unit test (we could run the unit test with the $\textbf{sbt test}$ command) \cite{OD16}.

@@

\section{Conclusions}

@@

Since all the $\textit{NP--complete}$ optimization problems become easy, everything will be much more efficient \cite{LF09}. Transportation of all forms will be scheduled optimally to move people and goods around quicker and cheaper \cite{LF09}. Manufacturers can improve their production to increase speed and create less waste \cite{LF09}.

Learning becomes easy by using the principle of Occam's razor: We simply find the smallest program consistent with the data \cite{LF09}. Near perfect vision recognition, language comprehension and translation and all other learning tasks become trivial \cite{LF09}. We will also have much better predictions of weather and earthquakes and other natural phenomenon \cite{LF09}.

The economy would become vastly more efficient. There would be disruption, including maybe displacing programmers \cite{IMP95}. The practice of programming itself would be more about gathering training data and less about writing code \cite{IMP95}. Google would have the resources to excel in such a world \cite{IMP95}.
